\documentclass[a4paper,10pt]{article}

% Load the shared config.tex
\input{config.tex}

\begin{document}

% Header with your information
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{Rodrigo Manuel Navarro Lajous} & \today \\  % Date of the letter
    \href{mailto:your.email@example.com}{your.email@example.com} & \\
    \href{https://www.linkedin.com/in/rodrigo-manuel-navarro-lajous/}{linkedin.com/in/rodrigo-manuel-navarro-lajous} & +123-456-7890 \\
    \href{https://www.navarrolajous.com}{navarrolajous.com} & \\
\end{tabular*}

\vspace{1cm}

% Contact Name (optional if you don't have a name)
% Contact Title
% Company Name
% Street Address
% City, State, Zip Code
\textbf{Hiring Manager} \\  % Use "Hiring Manager" if the contact name is not available
{Company Name} \\
{Company Address} \\
{City, State, ZIP Code} \\

\vspace{1cm}

% Address to a particular person if possible and remember to use a colon
Dear {Hiring Manager's Name},  % Optional: Use complete title and address (if you need to save space, you can omit the full address)

\vspace{0.5cm}

% Opening paragraph:
% Clearly state why you’re writing, name the position or type of work you’re exploring and, where applicable, how you heard about the position or organization.
% A summary statement may work well here by including three reasons you think you would be a good fit for the opportunity.
% Optional: Be brief, but specific.
I am writing to express my interest in the {Job Title} position at {Company Name}. I learned about this opportunity through {mention source}, and I believe my {mention three key strengths} make me a strong candidate for this role. I am eager to explore how my background aligns with {Company Name}’s mission and goals.

\vspace{0.5cm}

% Middle paragraph(s):
% Explain why you are interested in this employer and your reasons for desiring this type of work.
% If you’ve had relevant school or work experience, be sure to point it out with one or two key examples; but do not reiterate your entire resume.
% Emphasize skills or abilities that relate to the job. Be sure to do this in a confident manner and remember that the reader will view your letter as an example of your writing skills.
% Optional: Make the addressee want to read your resume.
I am particularly interested in this position because {explain why you are interested in the employer and the role}. During my time at {mention relevant work or academic experience}, I developed key skills such as {mention 1-2 specific skills or experiences} that directly relate to the responsibilities of this position. These experiences have sharpened my ability to {mention a key professional trait} while contributing meaningfully to my team.

I am confident that my experience with {mention a relevant project or task} will allow me to effectively contribute to {Company Name}’s ongoing projects. I am excited about the possibility of applying these skills in your organization’s {mention a specific aspect of the job or company}.

\vspace{0.5cm}

% Closing paragraph:
% Reiterate your interest in the position, and your enthusiasm for using your skills to contribute to the work of the organization.
% Thank the reader for their consideration of your application, and end by stating that you look forward to the opportunity to further discuss the position.
% Optional: Remind the reader of what you can do for the organization.
I am eager to bring my {mention a key strength or skill} to your team, and I am confident that my contributions would support {Company Name}’s vision and objectives. Thank you for considering my application. I look forward to the opportunity to further discuss how my skills and experiences align with your needs.

\vspace{0.5cm}

% Sincerely,
% Your name typed (Use a proper sign-off)
Sincerely, \\
Rodrigo Manuel Navarro Lajous

\end{document}
