\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Software Engineer}{May 2021 -- Present}
      {POAP}{Remote}
      \resumeItemListStart
        \resumeItem{Migrated the entire architecture to AWS CloudFormation, implementing CI/CD pipelines that streamlined deployments and enhanced the scalability and reliability of the system.}
        \resumeItem{Created and published POAP.js, an open-source library that streamlined integration with our ecosystem, becoming a key internal tool and significantly improving developer efficiency.}
        \resumeItem{Implemented Freeze Token functionality on the Upgradable POAP Smart Contract, enhancing token migration security.}
        \resumeItem{Improved development time by implementing an internal tooling for deploying all our services to multiples Api Gateways.}
        \resumeItem{\textbf{Leveraged Knowledge:} AWS, CloudFormation, CI/CD, Solidity, TypeScript, HardHat, Jest, Blockcahin, Web3 }
      \resumeItemListEnd

\resumeSubheading
  {Full Stack Developer}{Apr. 2020 -- May 2021}
  {Quipu Market}{Remote}
  \resumeItemListStart
    \resumeItem{Implemented and delivered courses that improved new developers' ramp-up time, reducing training time by half.}
    \resumeItem{Created a public component library that accelerated development time by 30\% across multiple projects.}
    \resumeItem{Designed and implemented CI/CD pipelines, streamlining deployment processes and improving code reliability.}
    \resumeItem{\textbf{Leveraged Knowledge:} CSS, Front-end Design Systems, JavaScript, Library Development, CI/CD.}
  \resumeItemListEnd


\resumeSubheading
  {Full Stack Developer}{Oct. 2019 -- Apr. 2020}
  {Turismocity}{Buenos Aires, Argentina}
  \resumeItemListStart
    \resumeItem{Led the integration of proprietary and external APIs, improving data consistency and system reliability.}
    \resumeItem{Collaborated with stakeholders to ensure the API integration met business needs and user expectations.}
    \resumeItem{\textbf{Leveraged Knowledge:} API Development, Stakeholder Management, Front-end Design, System Integration.}
  \resumeItemListEnd


  \resumeSubHeadingListEnd
